Demers Cartogram with Rivers

### 2023-09-27 paper/main.tex
fix: footnote

\textbf{P2:} The participants are given three practice tasks to familiarize themselves with the user study design.
A sample task is shown in \Cref{fig:task}, and accessible at \url{https://ghr.wangqiru.com/#/P1} and included in the online materials \footnotemark{}.
\new{The practice tasks are identital to the actual tasks, accompanied by instructions provided before the actual tasks commence.
The results from these practice tasks are not included in the final analysis.}
These tasks also serve as a quality test to see whether users are taking the study seriously.
A demonstration of three sample tasks is also included in the instructional video.

\textbf{P3:} The participants are asked to complete 16 location tasks that involve 4 targetCCGs.
\new{See the online materials for exact locations of target CCGs \footnotemark{}.}
Response and reaction time are recorded.
These 4 CCGs are selected to avoid extreme cases (thus bias the result), in terms of size, color, and location.

\textbf{P4:} The participants are asked to complete a questionnaire that consists of \new{5-Point} Likert Scale questions and open-ended questions.

>>>>

\textbf{P2:} The participants are given three practice tasks to familiarize themselves with the user study design.
A sample task is shown in \Cref{fig:task}, and accessible at \url{https://ghr.wangqiru.com/#/P1} and included in the online materials\footnotemark{}.
\new{The practice tasks are identital to the actual tasks, accompanied by instructions provided before the actual tasks commence.
The results from these practice tasks are not included in the final analysis.}
These tasks also serve as a quality test to see whether users are taking the study seriously.
A demonstration of three sample tasks is also included in the instructional video.

\textbf{P3:} The participants are asked to complete 16 location tasks that involve 4 targetCCGs.
\new{See the online materials for exact locations of target CCGs\footnotemark[\value{footnote}].}
Response and reaction time are recorded.
These 4 CCGs are selected to avoid extreme cases (thus bias the result), in terms of size, color, and location.

\textbf{P4:} The participants are asked to complete a questionnaire\footnotemark[\value{footnote}] that consists of \new{5-Point} Likert Scale questions and open-ended questions.
